Automating Verification of MPC Security: $\metaprot$ to $\minifed$

### 2023-07-10 popl24/main.tex
checkpoint

\usepackage{amsmath}
\usepackage{amstext}
\usepackage{fp-frame}
\usepackage[latin1]{inputenc}
\usepackage{mathpartir}
\usepackage{fancyvrb}
\usepackage{moreverb}
\usepackage{stmaryrd}
\usepackage{enumerate}

@@

\author{Author names withheld for double-blind reviewing.}

\begin{abstract}
  We formulate a sound hyperproperty of MPC passive security and show how this
  supports automated and semi-automated verification.
\end{abstract}

@@

@@

>>>>

\usepackage{amsmath}
\usepackage{amstext}
\usepackage{fp-frame}
\usepackage[latin1]{inputenc}
\usepackage{mathpartir}
\usepackage{fancyvrb}
\usepackage{moreverb}
\usepackage{stmaryrd}
\usepackage{enumerate}
\usepackage{thmtools,thm-restate}
\usepackage{comment}

@@

\author{Author names withheld for double-blind reviewing}

\begin{abstract}
Secure Multi-Party Computation (MPC) protocols support data privacy in
important modern distributed applications. Security for MPC protocols
is superficially similar to probabilistic noninterference, but differs
in a subtle but fundamental way, and approaches for verifying
noninterference cannot naturally extend to MPC security.  Currently,
proof methods for MPC protocols are well-studied but manual
and thus tedious and error-prone, and are also non-standardized and
unfamiliar to most PL theorists.  Our goal is to strengthen
connections between the security model of MPC and trace-based
hyperproperties, and to leverage them to obtain automated
enforcement mechanisms for MPC protocol development.  We define a
novel hyperproperty that is provably sound for MPC security, as a
foundation for fully and partially automated verification of passive
MPC security in protocols including arbitrarily large YGC and GMW
circuits.
\end{abstract}

@@

\input{automation}

%% This is scratch pad to develop ideas before integration.
%\input{scratch}

\appendix

\input{ygc}

@@

\input{proofs}
